---
title: "CIS Code Sheet"
author: "Arnab"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
    default_style: "light"
    downcute_theme: "default"
    number_sections: TRUE
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dependencies, message=FALSE, warning=FALSE}
library("foreign")
library("dplyr")
library("tidyr")
library("knitr")
library("DT")
```

# Preprocessing Data

We will look at the data year-wise before constructing the panel.

## 1992

### NFHS 1 Household Member Recode.

We have selected the variables

1.  state

2.  male

3.  age

4.  years of education

5.  caste (not used)

religion (not available)

```{r}
nfhs1992hr <-
  read.dta("raw data/NFHS/NFHS 1992 HM Recode/IAPR23FL.DTA") |>
  select(
    sex = hv104,
    age = hv105,
    edu = hv108,
    state = hv024,
    caste = shcaste,
  ) |> 
  mutate(
    male = factor(
      sex, 
      levels = c(1, 2), 
      labels = c(1, 0)
      ),
    caste = factor(
      caste, 
      levels = c("scheduled caste", "scheduled tribe", "other"),
      labels = c("SC", "ST", "Oth")
    ),
    edu = case_match(
      edu,
      97 ~ NA,
      99 ~ NA,
      98 ~ NA,
      .default = edu),
    age = case_match(
      age,
      98 ~ NA,
      .default = age),
    state = factor(
      case_match(
      state,
      "arunachalpradesh" ~ "arunchal pradesh",
      .default = state
    )
    ))

datatable(sample_n(nfhs1992hr, size = 100), rownames = F)
```

TODO: Data too big to be shown. Will show a random sample later.

### NFHS 1 Individual (Women) Recode.

Have not done this yet. Need to look at possible women autonomy factors.

### Aggregating to State Level

For now, taking the following variables:

1.  mean years of female education.
2.  mean years of male education.
3.  sex ratio. (number of women per 1000 men)
4.  mean female age.
5.  mean male age.
6.  state

```{r message=FALSE, warning=FALSE}
statelevel1992 <- 
  nfhs1992hr |> 
    select(
      state,
      edu,
      male,
      age
    ) |> tidyr::drop_na() |> 
    group_by(state, male) |> 
    summarise(
      edu = mean(edu),
      age = mean(age),
      count = n()
    ) |> pivot_wider(
      names_from = male,
      values_from = c(edu, age, count)
    ) |> 
    mutate(
      state,
      medu = edu_1,
      fedu = edu_0,
      mage = age_1,
      fage = age_0,
      sratio = 1000 * count_0/count_1,
      .keep = "none",
    )

rm(nfhs1992hr)
```

Adding in the crime data

Note that we do not use Jammu as NFHS collected data for Jammu while NCRB data is for Jammu and Kashmir.

Delhi vs New Delhi issue.

1. Population is in lakhs.
2. Incidence is number of crime against women per 1 lakh pop.

```{r}
crime1992 <- read.csv("raw data/NCRB/crime1992.csv")
statelevel1992 <- inner_join(statelevel1992, crime1992, by = 'state')
rm(crime1992)

datatable(statelevel1992, rownames = F)
```

## 1998

### NFHS 2 Household Member Recode.

We have selected the variables

1.  state

2.  male

3.  age

4.  years of education

5.  caste (not used)

6.  religion (not used)

```{r}
nfhs1998hr <- 
  read.dta("raw data/NFHS/NFHS 1998 HM Recode/IAPR42FL.DTA") |> 
  select(
    state = hv024,
    male = hv104,
    age = hv105,
    edu = hv108,
    caste = sh41,
    rel = sh39
  ) |> 
  mutate(
    male = factor(
      male, 
      levels = c("male", "female"),
      labels = c(1, 0)
    ),
    caste = factor(
      caste,
      levels = c(
        "scheduled caste", 
        "scheduled tribe", 
        "obc", 
        "other"
      ),
      labels = c("SC", "ST", "OBC", "Oth")
    ),
    edu = case_match(
      edu,
      97 ~ NA,
      99 ~ NA,
      98 ~ NA,
      .default = edu),
    age = case_match(
      age,
      98 ~ NA,
      .default = age),
    rel = factor(rel),
    state = factor(
      case_match(
      state,
      "arunachalpradesh" ~ "arunchal pradesh",
      .default = state
    )
    )
  )

datatable(sample_n(nfhs1998hr, size = 100), rownames = F)
```
<table style="text-align:center"><tr><td colspan="6" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left">Statistic</td><td>N</td><td>Mean</td><td>St. Dev.</td><td>Min</td><td>Max</td></tr>
<tr><td colspan="6" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left">age</td><td>517,313</td><td>25.472</td><td>19.161</td><td>0</td><td>95</td></tr>
<tr><td style="text-align:left">edu</td><td>516,098</td><td>4.099</td><td>4.644</td><td>0</td><td>24</td></tr>
<tr><td colspan="6" style="border-bottom: 1px solid black"></td></tr></table>

### NFHS 2 Individual (Women) Recode.

### Aggregating to State Level

```{r message=FALSE, warning=FALSE}
statelevel1998 <- 
  nfhs1998hr |> 
    select(
      state,
      edu,
      male,
      age
    ) |> tidyr::drop_na() |> 
    group_by(state, male) |> 
    summarise(
      edu = mean(edu),
      age = mean(age),
      count = n()
    ) |> pivot_wider(
      names_from = male,
      values_from = c(edu, age, count)
    ) |> 
    mutate(
      state,
      medu = edu_1,
      fedu = edu_0,
      mage = age_1,
      fage = age_0,
      sratio = 1000 * count_0/count_1,
      .keep = "none",
    )

rm(nfhs1998hr)
```
Adding in the crime data

Note that we do not use Jammu as NFHS collected data for Jammu while NCRB data is for Jammu and Kashmir.

1. Population is in lakhs.
2. Incidence is number of crime against women per 1 lakh pop.

Adding in the crime data

```{r}
crime1998 <- read.csv("raw data/NCRB/crime1998.csv") 
statelevel1998 <- inner_join(statelevel1998, crime1998, by = 'state')
rm(crime1998)

datatable(statelevel1998, rownames = F)
```

## 2005

### NFHS 3 Household Member Recode.
```{r message=FALSE, warning=FALSE}
nfhs2005hr <-
  read.dta("raw data/NFHS/NFHS 2005 HM Recode/IAPR52FL.DTA") |>
  select(
    state = hv024,
    male = hv104,
    age = hv105,
    edu = hv108,
    caste = sh46,
    rel = sh44
  ) |> 
  mutate(
    male = factor(
      male, 
      levels = c("male", "female"), 
      labels = c(1, 0)
    ),
    caste = factor(
      caste, 
      levels = c(
        "scheduled caste", 
        "scheduled tribe", 
        "other backward class", 
        "none of above"
        ),
      labels = c("SC", "ST", "OBC", "Oth")
    ),
    edu = case_match(
      edu,
      97 ~ NA,
      99 ~ NA,
      98 ~ NA,
      .default = edu),
    age = case_match(
      age, 
      98 ~ NA,
      .default = age
    ),
    rel = factor(rel),
    state = factor(substring(state, 6))
  )

datatable(sample_n(nfhs2005hr, size = 100), rownames = F)
```



### NFHS 3 Individual (Women) Recode.

### Aggregating to State Level

```{r message=FALSE, warning=FALSE}
statelevel2005 <- 
  nfhs2005hr |> 
    select(
      state,
      edu,
      male,
      age
    ) |> tidyr::drop_na() |> 
    group_by(state, male) |> 
    summarise(
      edu = mean(edu),
      age = mean(age),
      count = n()
    ) |> pivot_wider(
      names_from = male,
      values_from = c(edu, age, count)
    ) |> 
    mutate(
      state,
      medu = edu_1,
      fedu = edu_0,
      mage = age_1,
      fage = age_0,
      sratio = 1000 * count_0/count_1,
      .keep = "none",
    )

rm(nfhs2005hr)
```

Adding in the crime data

Note that we do not use Jammu as NFHS collected data for Jammu while NCRB data is for Jammu and Kashmir.

from here, Delhi is delhi.

1. Population is in lakhs.
2. Incidence is number of crime against women per 1 lakh pop.

```{r}
crime2005 <- read.csv("raw data/NCRB/crime2005.csv") 
statelevel2005 <- inner_join(statelevel2005, crime2005, by = 'state')
rm(crime2005)
datatable(statelevel2005, rownames = F)
```

## 2015

### NFHS 4 Household Member Recode.

### NFHS 4 Individual (Women) Recode.

### Aggregating to State Level

## 2021

### NFHS 5 Household Member Recode.

### NFHS 5 Individual (Women) Recode.

### Aggregating to State Level

## Constructing Panel

# Regression analysis


## Notes on Regression

FE
FEGLS
FD
Robust standard errors.

Non negative response
- log tranformation.
- Poisson regression for modelling the number of crime.
- Gamma regression for modelling incidence.

## Pooled OLS

### Level - Level Model

### Level - Log Model

### Log - Level Model

### Log - Log Model

## First Difference

### Level - Level Model

### Level - Log Model

### Log - Level Model

### Log - Log Model

## Fixed Effects

### Level - Level Model

### Level - Log Model

### Log - Level Model

### Log - Log Model

## Correlated Random Effects

For the time coefficient.

### Level - Level Model

### Level - Log Model

### Log - Level Model

### Log - Log Model
